The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-24 Results/pipeline.tex
fixed todos in evaluation
added the exploitation evidence section

\subsection[The Pipeline]{Understanding the Pipeline}
This section serves to represent our pipeline quantitatively and graphically. Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

@@

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability.
\input{Results/pipeline_table}

>>>>

\subsection[The Pipeline]{Understanding the Data Pipeline}
%This section serves to represent our pipeline quantitatively and graphically. 
Table~\ref{tab:pipeline} showcases the data gathered by our pipeline, with the differential changes at each stage of the pipeline.

@@

In our fuzzing attempts, the same behavior is repeated. We fuzzed \fuzzed\ forms with the regular payload, which resulted in a total of \recd\ e-mails (\recdDelta). After analysis of the received e-mails, we further fuzzed \fuzzed\ forms, which resulted in \success\ e-mails (\successDelta) which contain the vulnerability across \ips IP Addresses corresponding to \domains domains.
\input{Results/pipeline_table}
